### 2018-01-09 thesis/contents/reviews/trigeminal.tex
changes with moji

Modern pain literature continues to update the exactly diagnostic definition of TN. The Burchiel classification scheme divides facial pain into 5 major subtypes \cite{Burchiel2003,Eller2005}: idiopathic (without apparent cause), trigeminal injury, symptomatic, postherpetic, and atypical facial pain. Idiopathic TN has 2 sub-types: 1) TN type 1, also referred to as classic TN, where the patient experiences greater episodic pain greater than 50\% of the time; 2) TN type 2, where constant pain occurs greater than 50\% of the time. Trigeminal injury can be unintentional: which can be due to facial trauma, surgery to the oral cavity; this type of pain would involve persistent and burning pain to the affected areas; and is termed trigeminal neuropathic pain. The injury can also be intentional: due to interventions such as rhizotomy or gangliolysis; these result in numbness and loss of sensation of the face; and is termed trigeminal deafferentation pain. Symptomatic TN, also termed MS-TN, is due to trigeminal nerve injury relating to multiple sclerosis related central white matter inflammation. Postherpetic TN is pain resulting from the infection of the herpes zoster virus, and can involve burning pain and deafferentation. In this classification, the definition of atypical facial pain is reserved for somatoform pain disorder that can be of psychosomatic origin, although some literature can also include constant pain in the face into this classification. This is in contrast with the common clinical definition, where atypical facial pain is used for the definition of trigeminal pain whose symptomatology deviates from classic TN.

@@

There is also a definition \cite{Zakrzewska2016} that attempts to address the lack of symptomatic TN classification in ICHD-3 by classifying TN into idiopathic TN: without apparent cause; classic TN: caused by vascular compression of the trigeminal nerve root; and secondary TN: as the consequence of a major neurological disease such as MS.

@@

The sensory afferents include the myelinated A and unmyelinated C-fibers that originate from the subcutaneous sensory receptors responsible for mechano and temperature pain, fine touch and vibration, such as the Messner's corpuscles, Pacinian and Ruffini corpuscles.

The V1 branch provides the sensory innervation to the superior aspects of the face and cranium, including forehead, upper eyelids, eyeball, frontal sinus, lacrimal gland, and dura of the anterior cranial fossa. It further divides into lacrimal, frontal, and nasociliary nerve branches. The lacrimal branch supplies the lacrimal; the frontal contains smaller branches that innervate the skin of the medial forehead, upper eyelid, and parts of the frontal sinus; the nasociliary branch innervate various parts of the eye, and mucous membrane of the anterior nasal septum, anterior portion of the lateral nasal wall, and the skin on the tip of the nose. V1 enters the skull base through the superior orbital fissure.

The V2 provides innervation to the temple, cheek, lateral aspects of the nose, and lower eyelids via the zygomaticofacial and zygomaticotemporal branches. It also innervates upper oral cavity. It exists the skull through the foramen rotundum.

V3 contains sensory and motor branches. It innervates skins of the jaw, areas above the ear, lips, gum, and teeth. The V3 division carries the mastication efferent to the four muscles recruited for mastications: the masseter, temporal, medial and lateral pterygoids. The tensor tympani also receives some CN V innervation, which is thought to be important in dampening the sound of chewing. V3 exists the skull through foramen ovale.

The branches then converge and form the trigeminal root gangion (TRG) (also known as Gasserian, or semilunar ganglion), whose posterior extension forms the CN V. It is analogous to the spinal dorsal root ganglion, and contains all the trigeminal sensory cell bodies. It situates in the Meckel's cave, on the petrous bone of the middle cranial fossa. It is somatotopically organized in respect to the trigeminal branches, with V1 situated in medial anterior, V2 in caudal lateral, and V3 in the middle.

The extension of the posterior aspect of the TRG forms the trigeminal nerve body, with both sensory and motor roots. The nerve body straddles the TRG and the trigeminal nucleus, by crossing the pontine cistern. The portion of the sensory nerve that enters the pons is termed the trigeminal root entry zone (REZ). The cistern trigeminal sensory nerve, similar to other peripheral nerves, is myelinated by Schwann cells. The myelin cell type transitions to oligodendrocyte myelinations in the CNS as it enters the pons. The CNS myelin can be several millimetres beyond the surface of the pons, before it gives away to the transition area, termed root entry zone, or less commonly, Obersteiner-Redlich zone \cite{Peker2006}. Study in 100 CN V samples from 50 cadavers showed that cisternal CN V length ranges from 8-15 mm; the transition zone length is shorter on the medial aspect (0.1-2.5 mm) than the lateral aspect (0.17-6.75 mm). The transition zone can be up to 25\% of the nerve length \cite{Peker2006}.

@@

Classic TN is believed to be caused by neurovascular compression (NVC) of the CN V at its root entry zone (REZ) by the surrounding vasculature, where the nerve interfaces with the pons. An aberrant loop of artery and less commonly a vein is seen in 80-90\% of the cases of TN compressing the nerve \cite{Love2001,McLaughlin1999}. This can also be observed in conventional MR imaging \cite{Borges2010}. The superior cerebellar artery is responsible for most of the NVC (60-90\%), followed by the anteroinferior cerebellar artery and basilar arteries (Lutz et al., 2011). There is a slight lateral prevalence, with right-sided TN occurring in  in 60\% of the cases, and in rare cases may be related to asymmetries of the foramen rotundum and foramen ovale \cite{Toda2009}.  Other types of compressions may also cause TN; these can be in the forms of saccular aneurysm, arteriovenous malformation, vestibular schwannomas, meningiomas, epidermoid cysts, and other tumours.  However NVC cannot be assumed to be directly causal of TN, since observation of vascular compression does not necessarily result in the expression of pain \cite{Desouza2013,Hodaie2013}. In some cases the TN pain is reported to be contralateral to the NVC \cite{Cheng2008,Haddad1990,Revuelta1995}. There are also 10-15\% of cases where TN occurs with no observable vascular compression \cite{Revuelta-Gutierrez2006,Maarbjerg2015}.

The NVC that occurs in TN is believed to disrupt the central myelin, and that the region of disruption would begin at the peripheral-central myelin transition zone, and extending into central myelin regions. Janetta \cite{Jannetta1967} proposed that NVC leads to focal demyelination of the trigeminal sensory root axons, and causes ephaptic nerve conductances that cause neuralgia. Ultrastructural examinations \cite{Love1998} of tissue samples obtained from CN V rhizotomy specimens showed oligodendrocyte demyelination at the site of root transition zone. Adjacent to the site of compression-related focal demyelination, thinly myelinated sheaths that encapsulate a number of demyelinated axons could be observed, suggesting aberrant remyelination. The TRG is also postulated to be responsible for neuralgia \cite{Rappaport1994}. It's believed that ganglionic ectopic autonomic firing can be triggered by mechanical disturbances as a result of nerve compression. Additionally, ganglionic cross aftercharge may occur as a result of repeated stimulations in the nerve injury site, which ignites surrounding ganglionic neurons. Histology findings by Devor et al. supported the ignition hypothesis \cite{Devor2002a}, where demyelinated axons were shown to be in close apposition without intervening glia.

@@

The initial mode of treatment of TN consists in pharmacotherapy, primarily using anticonvulsant medication such as carbamazepine. While there is an initial, very good response to medical treatment, eventually nearly 50\% of patients will fail medical therapy, either due to side effects, or requirements of a progressive increase in dose \cite{Rappaport1994}. Multiple surgical treatments are available, from more central procedures addressing NVC to peripheral procedures such as neurectomy. The procedure that provides the greatest likelihood of pain relief is microvascular decompression (MVD) \cite{Lovely1997}, where the nerve is decompressed from the offending vascular structure through the placement of a piece of Teflon\textcopyright gauze. This is thought to dampen the pulsations of the artery on the nerve. MVD showed 90\% pain relief immediately after surgery \cite{Zakrzewska2005}, and a long-term success rate of 70\% at 10 years \cite{Barker1996}.
Partial sensory rhizotomy (PSR) can also be performed, where the offending CN V branch is severed, with a response rate of 88-70\% \cite{Young1993,Zakrzewska2005}.

Intervention can also be non-invasive, in the form of Gamma Knife radiosurgery (GKRS) \cite{Hodaie2012g}. The Perfexion GK system focuses gamma radiation from 192 cobalt-60 ($^{60}$Co) sources onto specific targets along the trigeminal nerve. The target is either on the cisternal segment of CN V or just outside of the REZ \cite{Daugherty2015}. Proximal targets correlate with longer pain relief, but also higher chance of facial numbness\cite{Xu2014}. The procedure requires a stereotactic frame, and a dose of 70-90 Gy is deposited. The effect is delayed and pain relief can be experienced in 4-6 weeks post-radiosurgery. GKRS treatments result in 90\% initial pain relief \cite{Tuleasca2015,Kondziolka2010}, about 50-80\% pain-free at 1 year, 45-65\% 2 years and 30-40\% 3 years after surgery \cite{Kondziolka2010,Sheehan2005}. More recent studies suggested higher pain-free probabilities at 3(71.8\%), 5(64.9\%), 7(59.7\%) and 10(45.3\%) years\cite{Tuleasca2015}. More favourable treatment outcomes were related to no other accompanying symptoms, no prior surgery and shorter term pain history of fewer than three years.

>>>>

Modern pain literature continues to update the exact diagnostic definition of TN. The Burchiel classification scheme divides facial pain into 5 major subtypes \cite{Burchiel2003,Eller2005}: idiopathic (without apparent cause), trigeminal injury, symptomatic, postherpetic, and atypical facial pain. Idiopathic TN has 2 sub-types: 1) TN type 1, also referred to as classic TN, where the patient experiences greater episodic pain greater than 50\% of the time; 2) TN type 2, where constant pain occurs greater than 50\% of the time. Trigeminal injury can be unintentional: which can be due to facial trauma, surgery to the oral cavity; this type of pain would involve persistent and burning pain to the affected areas; and is termed trigeminal neuropathic pain. The injury can also be intentional, due to interventions such as rhizotomy or gangliolysis; these result in numbness and loss of sensation of the face and are termed trigeminal deafferentation pain. Symptomatic TN, also termed MS-TN, is due to trigeminal nerve injury relating to multiple sclerosis related central white matter inflammation. Postherpetic TN is pain resulting from the infection of the herpes zoster virus, and can involve burning pain and deafferentation. In this classification, the definition of atypical facial pain is reserved for somatoform pain disorder that can be of psychosomatic origin, although some literature can also include constant pain in the face into this classification. This is in contrast with the common clinical definition, where atypical facial pain is used for the definition of trigeminal pain whose symptomatology deviates from classic TN.

@@

There is also a definition \cite{Zakrzewska2016} that attempts to address the lack of symptomatic TN classification in ICHD-3 by classifying TN into idiopathic, classic TN, caused by vascular compression of the trigeminal nerve root and secondary TN, as the consequence of a major neurological disease such as MS.

@@

The sensory afferents include the myelinated A and unmyelinated C-fibers that originate from the subcutaneous sensory receptors responsible for mechano- and temperature pain, fine touch and vibration, such as the Messner's, Pacinian and Ruffini corpuscles.

The V1 branch provides the sensory innervation to the superior aspects of the face and cranium, including forehead, upper eyelids, eyeball, frontal sinus, lacrimal gland, and dura of the anterior cranial fossa. It further divides into lacrimal, frontal, and nasociliary nerve branches. The lacrimal branch supplies the lacrimal gland; the frontal contains smaller branches that innervate the skin of the medial forehead, upper eyelid, and parts of the frontal sinus; the nasociliary branch innervate various parts of the eye, and mucous membrane of the anterior nasal septum, anterior portion of the lateral nasal wall, and the skin on the tip of the nose. V1 exits the skullbase through the superior orbital fissure.

The V2 provides innervation to the temple, cheek, lateral aspects of the nose, and lower eyelids via the zygomaticofacial and zygomaticotemporal branches. It also innervates upper oral cavity. It exits the skull through the foramen rotundum.

V3 contains sensory and motor branches. It innervates skins of the jaw, areas above the ear, lips, gum, and teeth. The V3 division carries the mastication efferent to the four muscles recruited for mastications: the masseter, temporal, medial and lateral pterygoids. The tensor tympani also receives some CN V innervation, but it is primarily innervated by the facial nerve.  It is thought that CNV innervation is important in dampening the sound of chewing. V3 exits the skull through foramen ovale.

The afferent branches converge and form the trigeminal root gangion (TRG) (also known as Gasserian, or semilunar ganglion), which then forms the trunk or cisternal component of CN V. The TRG contains all the trigeminal sensory cell bodies. It situates in the Meckel's cave, in the middle cranial fossa. It is anatomically organized with respect to the trigeminal branches, with V1 situated in medial anterior, V2 in caudal lateral, and V3 in the middle.

The extension of the posterior aspect of the TRG forms the trigeminal nerve body, with both sensory and motor roots. The nerve body straddles the TRG and the trigeminal nucleus, by crossing the pontine cistern. The portion of the sensory nerve that enters the pons is termed the trigeminal root entry zone (REZ). The cistern trigeminal sensory nerve, similar to other peripheral nerves, is myelinated by Schwann cells. The myelin cell type transitions to oligodendrocyte myelinations in the CNS as it enters the pons. The CNS myelin can be several millimetres beyond the surface of the pons, before it gives away to the transition area, termed root entry zone, or Obersteiner-Redlich zone \cite{Peker2006}. Study in 100 CN V samples from 50 cadavers showed that cisternal CN V length ranges from 8-15 mm; the transition zone length is shorter on the medial aspect (0.1-2.5 mm) than the lateral aspect (0.17-6.75 mm). The transition zone can be up to 25\% of the nerve length \cite{Peker2006}.

@@

Classic TN is believed to be caused by neurovascular compression (NVC) of the CN V at its root entry zone (REZ) by the surrounding vasculature, where the nerve interfaces with the pons. An aberrant loop of artery and less commonly a vein is seen in 80-90\% of the cases of TN compressing the nerve \cite{Love2001,McLaughlin1999}. This can also be observed in conventional MR imaging \cite{Borges2010}. The superior cerebellar artery is responsible for most of the NVC (60-90\%), followed by the anterior inferior cerebellar artery (AICA) and basilar arteries \cite{Lutz2011}. There is a slight lateral prevalence, with right-sided TN occurring in  in 60\% of the cases, and in rare cases may be related to asymmetries of the foramen rotundum and foramen ovale \cite{Toda2009}.  Other types of compression may also cause TN; these can be in the forms of vestibular schwannomas, meningiomas, epidermoid cysts, and other cerebellopontine angle tumours, arteriovenous malformations and saccular aneurysms . However NVC cannot be assumed to be directly causal of TN, since observation of vascular compression does not necessarily result in the clinical expression of pain \cite{Desouza2013,Hodaie2013}. In approximately 10-15\% of cases where TN occurs with no observable vascular compression \cite{Revuelta-Gutierrez2006,Maarbjerg2015}.

Janetta \cite{Jannetta1967} proposed that NVC leads to focal demyelination of the trigeminal sensory root axons, and causes ephaptic nerve conductances that cause neuralgia. Ultrastructural examinations \cite{Love1998} of tissue samples obtained from CN V rhizotomy specimens showed oligodendrocyte demyelination at the site of root transition zone. Adjacent to the site of compression-related focal demyelination, thinly myelinated sheaths that encapsulate a number of demyelinated axons could be observed, suggesting aberrant remyelination. It is therefore plausible that NCV disrupts the central myelin. The region of disruption may include the peripheral-central myelin transition zone, and extending into central myelin regions.The TRG is also postulated to be responsible for neuralgia \cite{Rappaport1994}. It is believed that ganglionic ectopic autonomic firing can be triggered by mechanical disturbances as a result of nerve compression. Additionally, ganglionic cross aftercharge may occur as a result of repeated stimulations in the nerve injury site, which ignites surrounding neurons. Histological findings by Devor et al. support the ignition hypothesis \cite{Devor2002a}, where demyelinated axons are shown to be in close apposition without intervening glia.

@@

The initial mode of treatment of TN consists in pharmacotherapy, primarily using anticonvulsant medication such as carbamazepine. While there is an initial, very good response to medical treatment, eventually nearly 50\% of patients will fail medical therapy, either due to side effects, or requirements of a progressive increase in dose \cite{Rappaport1994}. Multiple surgical treatments are available, from more central procedures addressing NVC to peripheral procedures such as neurectomy. The procedure that provides the greatest likelihood of pain relief is microvascular decompression (MVD) \cite{Lovely1997,Hodaie2013}, where the nerve is decompressed from the offending vascular structure through the placement of a piece of Teflon\textcopyright gauze. This is thought to dampen the pulsations of the artery on the nerve. MVD can result in 90\% pain relief immediately after surgery \cite{Zakrzewska2005}, and a long-term success rate of 70\% at 10 years \cite{Barker1996}.
Partial sensory rhizotomy (PSR) can also be performed, where the offending CN V branch is severed, with a response rate of 88-70\% \cite{Young1993,Zakrzewska2005}.

Intervention can also be non-invasive, in the form of Gamma Knife radiosurgery (GKRS) \cite{Hodaie2012g}. The Perfexion GK system focuses gamma radiation from 192 cobalt-60 ($^{60}$Co) sources onto specific targets along the trigeminal nerve. The target is either on the cisternal segment of CN V or just outside of the REZ \cite{Daugherty2015}. Proximal targets correlate with longer pain relief, but also higher chance of facial numbness\cite{Xu2014}. The procedure requires a stereotactic frame, and a dose of 70-90 Gy delivered to the nerve. The effect is delayed and pain relief can be experienced in 4-6 weeks post-radiosurgery. GKRS treatments result in 75\% initial pain relief \cite{Tuleasca2015,Kondziolka2010}, about 50-80\% remain pain-free at 1 year, 45-65\% 2 years and 30-40\% 3 years after surgery \cite{Kondziolka2010,Sheehan2005}. More favourable treatment outcomes were related to no other accompanying symptoms, no prior surgery and shorter term pain history of fewer than three years.

\subsection{Neuroimaging of Trigeminal Neuralgia}

Neuroimaging of the TN has been challenging, due to the small diameter of the CN V and since the contrast of the CNS trigeminal pathways is difficult to distinguish from the surrounding on conventional MRI \cite{Borges2010}. Manual segmentation of T1 and T2 MRI requires great effort, with mixed results \cite{Miller2008a}. Diffusion MRI provided fiber orientation, and early attempts to segment the trigeminal system showed promise \cite{Upadhyay2008,Habas2007f}.

Application of tractography permitted visual reconstructions of human cranial nerves in vivo \cite{Hodaie2010}. Cisternal CN V could be reliably delineated with Gaussian tensors with just 25 MR gradient directions. This permitted high fidelity visualization and targeted characterization of CN V diffusivity in TN, demonstrating significant reduction in fractional anisotropy (FA) post-surgery at the site of the GK target \cite{Hodaie2009a}. Study of CN V diffusivity in conjunction with deep white matter using TBSS, again revealed reduced FA on the affected CN V, with also bilateral increased in radial, axial, and mean diffusivity. Disruptions were also found in the cognitive-affective, attention, and motor regions of the cortex, consistent with cortical patterns in chronic pain \cite{Desouza2013}. Lowered FA was reported in multiple TN studies \cite{Herweh2007, Lutz2011}. Study in temporomandibular disorder (TMD) showed a bilateral reduction in CN V FA compared to controls, with the FA of the affected side significantly inverse-correlates with pain duration \cite{Moayedi2012}, thereby demonstrating that CN V FA is related to nociception. The TMD study also revealed similar cognitive and motor disruption, and internal capsule FA significantly inverse-correlated with pain intensity.

### 2018-01-09 thesis/contents/tn_sagit.tex
changes with moji

\section{Abstract}
\textbf{Introduction:} Trigeminal Neuralgia (TN) is a debilitating facial pain syndrome that involves the trigeminal sensory pathway. We demonstrate the use of a fully-automated group white-matter tractography, and Gaussian Process (GP) classification to pinpoint key white-matter diffusivity changes that maximally differentiate patients and healthy controls.

\textbf{Methods:} We perform group merged tractography using SAGIT on 36 sex-matched TN patients (right-sided pain) and 36 controls. The trigeminal nerve (CN V), pontine decussation, and thalamocortical S1 pathways were reconstructed. GP classifiers were trained by scrolling a moving window over CN V and S1 tractography centroids. FA, GFA, RD, AD, and MD metrics were evaluated. Both TN vs. Control and Affect vs. Unaffected were analyzed. Classifiers that performed at greater-or-equal-to than 75\% accuracy were accepted.

\textbf{Results:} Both affected and unaffected CN V can be differentiated with up to 80\% accuracy from controls. Affected CN V differences were more focused in the cistern and root-transition-zone, whereas unaffected CN V show more focus towards the brainstem. The affected S1 showed focused MD differences towards the cortex with an accuracy of 85\%.

@@

Tractography was first performed in the native DWI space for each individual.  FA, AD, RD, MD, GFA and AP metrics were embedded into the native tractography models by sampling the corresponding images maps using the points of the tractography geometry with tri-linear interpolation. Additionally, subject ID and group ID scalar values were also inserted into each tractography files for identification.

@@

Diffusivity metrics of affected (right side) and unaffected CN V and S1 pathways were independently compared with those of controls, where control metrics were the average of both left and right sides. The affected and unaffected sides in TN patients were also compared with each other. 
Age was regressed out by using the residuals of the linear regression model from controls group. The diffusion values were subsequently normalized to zero mean with ranges $[-1, 1]$ for model training. 
Gaussian Process (GP) classification was exhaustively performed on CN V and S1 nerve segments to identify key segment differences. Multiple moving windows of length between 5 to 30 were used to constraint tract segments, and a Gaussian Process model was trained for each windowed segment. The entire machine learning process was performed using Scikit-learn machine learning software framework.
For each model, the subjects were split into train and validation sets using stratified 10-fold cross-validation. The GP model was initiated with Matern kernel (length scale = 1), and the model fitted using the training set. The validation set was used to measure prediction accuracy, and the mean accuracy of the 10-fold cross-validation was used to assess the windowed segment. Segments accuracy greater than 75\% were accepted, and the segment length with the greatest accuracy was then determined.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{CN V-inferior-view.png}
\caption{Inferior view of the merged CN V delineations.}
\label{fig:GPfigure1}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{figure-GP-CN V.pdf}
\caption{CN V classifier performance}
\label{fig:GPfigure4}
\end{figure}

\begin{table}[ht]
\centering
\csvautotabular{CN V_table.csv}
\caption{CN V GP classifier performance data}
\caption*{List of the best accuracy for each diffusion metric. Precision, recall, and f1 scores are also provided for reference}
\label{table:CN V}
\end{table}

>>>>

\section{Abstract}
\textbf{Introduction:} Trigeminal Neuralgia (TN) is a debilitating facial neuropathic pain syndrome involving the trigeminal sensory pathway. We demonstrate the use of a fully-automated group white-matter tractography, and Gaussian Process (GP) classification to pinpoint key white-matter diffusivity changes that maximally differentiate patients and healthy controls.

\textbf{Methods:} We performed group merged tractography using SAGIT on 36 sex-matched TN patients (right-sided pain) and 36 controls. The trigeminal nerve (CN V), pontine decussation, and thalamocortical S1 pathways were reconstructed. GP classifiers were trained by scrolling a moving window over CN V and S1 tractography centroids. FA, GFA, RD, AD, and MD metrics were evaluated. Both TN vs. Control and Affect vs. Unaffected were analyzed. Classifiers that performed at greater-or-equal-to 75\% accuracy were accepted.

\textbf{Results:} Both affected and unaffected trigeminal nerves in TN patients can be differentiated with up to 80\% accuracy from controls. Affected CN V differences were more focused in the cistern and root-transition-zone, whereas unaffected CN V show more focus towards the brainstem. The affected S1 showed focused MD differences towards the cortex with an accuracy of 85\%.

@@

Tractography was first performed in the native DWI space for each individual.  FA, AD, RD, MD, and GFA metrics were embedded into the native tractography models by sampling the corresponding images maps using the points of the tractography geometry with tri-linear interpolation. Additionally, subject ID and group ID scalar values were also inserted into each tractography files for identification.

@@

Diffusivity metrics of affected (right side) and unaffected CN V and S1 pathways were independently compared with those of controls, where control metrics were the average of both left and right sides. The affected and unaffected sides in TN patients were also compared with each other. 
Age was regressed out by using the residuals of the linear regression model from the controls group. The diffusion values were subsequently normalized to zero mean with ranges $[-1, 1]$ for model training. 
Gaussian Process (GP) classification was exhaustively performed on CN V and S1 nerve segments to identify key segment differences. Multiple moving windows of length between 5 to 30 were used to constraint tract segments, and a Gaussian Process model was trained for each windowed segment. The entire machine learning process was performed using Scikit-learn machine learning software framework.
For each model, the subjects were split into train and validation sets using stratified 10-fold cross-validation. The GP model was initiated with Matern kernel (length scale = 1), and the model fitted using the training set. The validation set was used to measure prediction accuracy, and the mean accuracy of the 10-fold cross-validation was used to assess the windowed segment. Segments accuracy greater than 75\% were accepted, and the segment length with the greatest accuracy was then determined.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{cnv-inferior-view.png}
\caption{Inferior view of the merged CN V delineations.}
\label{fig:GPfigure1}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=\linewidth]{figure-GP-CNV.pdf}
\caption{CN V classifier performance}
\label{fig:GPfigure4}
\end{figure}

\begin{table}[ht]
\centering
\csvautotabular{cnv_table.csv}
\caption{CN V GP classifier performance data}
\caption*{List of the best accuracy for each diffusion metric. Precision, recall, and f1 scores are also provided for reference}
\label{table:CN V}
\end{table}
